Local to Global Mariculture Modelling

### 2025-07-28 index.qmd
Functional responses to temperature

## Population and biomass

```{r raw biomass and weight data}
weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
biomass_cohort <- find_read(output_model_cohort_path, "biomass_stat_all_farms")
```

@@

```{r}
#| label: fig-functional-response-to-temperature
#| eval: false
#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.

@@

func_T_resp %>% 
  ggplot(aes(x = water_temp, y = ing_act)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
  # scale_y_continuous(breaks = seq(0,1.5,0.25)) +
  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Feedd ingested/provided") +
  prettyplot()
```

```{r}
#| label: patchwork-map-mercator
#| fig-cap: |
#|   Example of a patchwork
#| fig-height: 9
#| fig-width: 9.5

>>>>

```{r}
#| label: location-data

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id)
```

## Population and biomass {#sec-population-biomass}

```{r}
#| label: raw biomass and weight data

weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
biomass_cohort <- find_read(output_model_cohort_path, "biomass_stat_all_farms")
```

@@

@fig-functional-response-to-temperature shows the response of food ingested to temperature, and the food provided in response.

```{r}
#| label: fig-functional-response-to-temperature
#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dotted line), relative to maximum potential ingestion. The vertical dotted lines show the actual minimum and maximum daily temperatures experienced by farms represented in the model.

tar_load(farm_ts_data)
min_T <- min(farm_ts_data$temp_c)
max_T <- max(farm_ts_data$temp_c)

@@

max_ing <- max(func_T_resp$ing_act)

func_T_resp %>% 
  ggplot(aes(x = water_temp, y = ing_act/max_ing)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(y = food_prov/max_ing), linewidth = 0.75, linetype = "dotted") +
  geom_vline(xintercept = min_T, linetype = "dotted") +
  geom_vline(xintercept = max_T, linetype = "dotted") +
  # scale_y_continuous(breaks = seq(0,1.5,0.25)) +
  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Feedd ingested/provided") +
  prettyplot()
```

```{r}
#| label: patchwork-map-mercator
#| eval: false
#| fig-cap: |
#|   Example of a patchwork
#| fig-height: 9
#| fig-width: 9.5
